LOSA Fuel Poverty maps

### 2021-09-02 LSOA Fuel poverty.Rmd

head(df)
# select the places we want here
ggplot(df, aes(x='Proportion Over 65', y=`Proportion of households fuel poor (%)`)) +
  geom_point()

census_age$oldpop <- Census_age_fp$'Over 65s'/Census_age_fp$'Age: All usual residents; measures: Value'
ggplot(Census_age_fp, aes(x=oldpop, y=(`Proportion of households fuel poor (%)`/100)) +
  geom_point()
```

>>>>

head(df)
table(df$`LA Name`)
Solent <- dplyr::filter(df, `LA Name` == "Basingstoke and Deane"|
                           `LA Name` == "East Hampshire"|
                           `LA Name` == "Eastleigh"|
                           `LA Name` == "Fareham"|
                           `LA Name` == "Gosport"|
                           `LA Name` == "Hart"|
                           `LA Name` == "Havant"|
                           `LA Name` == "New Forest"|
                           `LA Name` == "Portsmouth"|
                           `LA Name` == "Rushmoor"|
                           `LA Name` == "Southampton"|
                           `LA Name` == "Test Valley"|
                           `LA Name` == "Winchester"|
                           `LA Name` == "Isle of Wight"
                           )

# select the places we want here
ggplot(Solent, aes(x=`Proportion Over 65`, y=`Proportion of households fuel poor (%)`)) +
  geom_point()
nrow(Solent)
table(Solent$`LA Name`)

```
